SST_patterns

### 2019-10-08 SST_patterns.Rmd
update

@@

plot_scat_func <- function(df){
  ggplot(data = df, aes(x = date_start, y = intensity_mean)) +
  geom_point() +
  scale_x_date(expand = c(0, 0)) +
  facet_wrap(~distance, ncol = 2) +
  theme_grey() +
  labs(y = "Mean Intensity", x = NULL)
}
(OISST_SP_plot <- plot_scat_func(df = OISST_SEAPOINT))
(OISST_SB_plot <- plot_scat_func(df = OISST_SB))
(OISST_PN_plot <- plot_scat_func(df = OISST_PN))
(OISST_LB_plot <- plot_scat_func(df = OISST_LB))
combined_OISST <- ggarrange(OISST_SP_plot, OISST_SB_plot, OISST_PN_plot,OISST_LB_plot)

@@

(OISST_SP_pl <- plot_loli_func(df = OISST_SEAPOINT))
(OISST_SB_pl <- plot_loli_func(df = OISST_SB))
(OISST_PN_pl <- plot_loli_func(df = OISST_PN))
(OISST_LB_pl <- plot_loli_func(df = OISST_LB))
combined_OISST_pl <- ggarrange(OISST_SP_pl, OISST_SB_pl, OISST_PN_pl,OISST_LB_pl)

@@

(CMC_SP_pl <- plot_loli_func(df = CMC_SEAPOINT))
(CMC_SB_pl <- plot_loli_func(df = CMC_SB))
(CMC_PN_pl <- plot_loli_func(df = CMC_PN))
(CMC_LB_pl <- plot_loli_func(df = CMC_LB))
combined_CMC_pl <- ggarrange(CMC_SP_pl, CMC_SB_pl, CMC_PN_pl,CMC_LB_pl)

>>>>

CMC_SP_plot <- CMC_SP_plot +
  ggtitle("Sea Point")
CMC_SB_plot <- CMC_SB_plot +
  ggtitle("Saldanha Bay")
CMC_PN_plot <- CMC_PN_plot +
  ggtitle("Port Nolloth")
CMC_LB_plot <- CMC_LB_plot +
  ggtitle("Lamberts Bay")

@@

plot_scat_func <- function(df){
  ggplot(data = df, aes(x = date_start, y = intensity_mean)) +
  geom_point() +
  scale_x_date(expand = c(0, 0)) +
  facet_wrap(~distance, ncol = 2) +
  theme_grey() +
  labs(y = "Mean Intensity", x = NULL)
}
(OISST_SP_plot <- plot_scat_func(df = OISST_SEAPOINT))
(OISST_SB_plot <- plot_scat_func(df = OISST_SB))
(OISST_PN_plot <- plot_scat_func(df = OISST_PN))
(OISST_LB_plot <- plot_scat_func(df = OISST_LB))

OISST_SP_plot <- OISST_SP_plot +
  ggtitle("Sea Point")
OISST_SB_plot <- OISST_SB_plot +
  ggtitle("Saldanha Bay")
OISST_PN_plot <- OISST_PN_plot +
  ggtitle("Port Nolloth")
OISST_LB_plot <- OISST_LB_plot +
  ggtitle("Lamberts Bay")

combined_OISST <- ggarrange(OISST_SP_plot, OISST_SB_plot, OISST_PN_plot,OISST_LB_plot)

@@

(OISST_SP_pl <- plot_loli_func(df = OISST_SEAPOINT))
(OISST_SB_pl <- plot_loli_func(df = OISST_SB))
(OISST_PN_pl <- plot_loli_func(df = OISST_PN))
(OISST_LB_pl <- plot_loli_func(df = OISST_LB))
OISST_SP_pl <- OISST_SP_pl +
  ggtitle("Sea Point")
OISST_SB_pl <- OISST_SB_pl +
  ggtitle("Saldanha Bay")
OISST_PN_pl <- OISST_PN_pl +
  ggtitle("Port Nolloth")
OISST_LB_pl <- OISST_LB_pl +
  ggtitle("Lamberts Bay")

combined_OISST_pl <- ggarrange(OISST_SP_pl, OISST_SB_pl, OISST_PN_pl,OISST_LB_pl)

@@

(CMC_SP_pl <- plot_loli_func(df = CMC_SEAPOINT))
(CMC_SB_pl <- plot_loli_func(df = CMC_SB))
(CMC_PN_pl <- plot_loli_func(df = CMC_PN))
(CMC_LB_pl <- plot_loli_func(df = CMC_LB))

CMC_SP_pl <- CMC_SP_pl +
  ggtitle("Sea Point")
CMC_SB_pl <- CMC_SB_pl +
  ggtitle("Saldanha Bay")
CMC_PN_pl <- CMC_PN_pl +
  ggtitle("Port Nolloth")
CMC_LB_pl <- CMC_LB_pl +
  ggtitle("Lamberts Bay")

combined_CMC_pl <- ggarrange(CMC_SP_pl, CMC_SB_pl, CMC_PN_pl,CMC_LB_pl)
